Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-24 manuscript/draft.Rmd
fix methods intro
we did not evaluate the long term forecasts

We evaluated 6 types of forecasting models (Table 1) at two time-scales. In the
first one, we divided our 32 years of data into 22 years of training data
and retained 10 years of data for evaluation via hindcasting. Second, we used
the full data set for training and made predictions through the year 2050. For
both time scales, we evaluated versions of each model with and without
correcting for observer effects, as described below.

>>>>

We evaluated 6 types of forecasting models (Table 1) by dividing the 32 years
of data into 22 years of training data and retained 10 years of data for 
evaluation via hindcasting. We also made long term forecasts by using the full
data set for training and making forecasts through the year 2050. For
both time scales, we made forecasts using each model with and without
correcting for observer effects, as described below.
